\begin{abstract}

    \begin{center}
        \textbf{Abstract}
    \end{center}

    In this scientific work the objective is to develop a security cashless payment method for a \acrfull{cba} that should be 
    installed near a camping place. Since more people are seeking a quieter place to spend their vacations, the idea of
    bringing a secure technological development to those areas can increase profit to the region. For this work we researched
    on \acrfull{nfc} and Smartcards. We describe their advantages and disadvantages and also their flaws and possible hardening
    measures. An interview will be conducted with two IT-Company based in Germany in order to understand how security measures
    are applied to their cashless payment methods. As empirical research we will conduct two experiments demonstrating security
    vulnerability and protection measures of the objects researched in this \textit{exposé}.

\end{abstract}
\begin{abstract} 
    \begin{center}
        \textbf{Zusammenfassung}
    \end{center}
    In dieser wissenschaftlichen Arbeit entwickeln ein sicheres bargeldloses Zahlungsverfahren für einen \acrshort{cba}, der auf
    einem Campingplatz installiert werden soll. Da immer mehr Menschen nach einem ruhigen Ort suchen,
    um ihren Urlaub zu verbringen, ist es sinnvoll eine sichere technische Entwicklung zu diesen Orten zu bringen, sodass 
    die Profit der Region zu steigern kann. In dieser Arbeit konzentrieren wir uns auf \acrshort{nfc} und auf Smartcards. 
    Wir beschreiben sowohl ihre Vor- und Nachteile als auch ihre Schwachstelle und Härtungsmaßnahmen. Wir führen auch ein Interview
    mit zwei IT-Firmen aus Deutschland, um ihre Sicherheitsimplementation besser zu verstehen.  Wir führen auch empirische 
    Experimenten, um die Verletzlichkeiten und Sicherung der Objekten dieser \textit{Exposé} darzustellen.  

    %\acrfull{nfc}

\end{abstract}
